Puyuma: Linux-based RTOS experimental platform for constructing self-driving miniature vehicles

### 2017-04-24 cthpc-2017/paper.tex
Fix typo
Write acknowledgement

Real-time performance is measured by stressing the system with LTP and applying cyclictest. We use LTP $-i$ and $-c$ flags to present the background CPU load with multiple processes and accessing on IO bus. Our customized Linux kernel brings better real-time ability in both user and kernel space, shown in Figure \ref{fig:xeno_perf_modify}. Table \ref{xeno_compare} records the maximum latency for Xenomai.

@@

>>>>

Real-time performance is measured by stressing the system with LTP and applying cyclictest. We use LTP $-i$ and $-c$ flags to specify the background CPU load with multiple processes and accessing on IO bus. Our customized Linux kernel brings better real-time ability in both user and kernel space, shown in Figure \ref{fig:xeno_perf_modify}. Table \ref{xeno_compare} records the maximum latency for Xenomai.

@@

\section{Acknowledge}

I begin my research in computer vision since I audited Prof. Nick Wang's lecture in National Chao Tung University in 2016, which is very inspiring.

After the class, our advisor Jim Huang, leads us doing the real-time robotic research, and make us gain a lot of new knowledges in computer vision, operating system, communiucation system, control theory, etc.

I want to thanks these professors, and my partners in National Cheng Kung University, especially Shao-Hua and Po-Sheng, without them, I would never able to achieve several key features of Puyuma.

I also want to thanks Providence University for providing me fundations and space doing experiments, and my parent, who let me receive education without any worries.
